COVID-19 and Online Learning Tools

### 2021-12-28 Paper_online_Learning.tex
updated methodology

In this work we also used Google Trend search quiries as a measurement proxy to investigate emerging evidence about distance learning and the popularity and the public interest in various distance education solutions. We used weekly Google Trend search quiries of various distance learning solutions during COVID-19 pandemic. We limited all of our searches to the period from 1 December 2019 to 15 August 2021 to match the period of COVID-19 pandemic. Through this we wanted to capture the volume of interest in the public realm about distance education solutions and how this changes over time.

Google Trends determines categories based on search patterns. According to \textcite{vaughan2014web} more relevant accurate data can be obtained by limiting the search in Google Trends to a specific category as it helps to reduce noise in the data. In this work our focus was given to education category. Google Trends does not provide the absolute search volume of a given search term. Instead it provides a relative search volume of a particular term adjusted according to the total searches of the geography and time range it represents. The resulted series scale from 0 to 100, where each data point in the series represents the search interest relative to the highest point on the series for the selected region and time. \autocite{alicino2015assessing,vaughan2014web}. As such, a value of 100 represents the peak popularity of the term.

It is important to decide what term to search for in Google Trends as different terms have different search volumes. In the past literature several strategies have been used to select suitable search terms for a given study. Some studies have selected search terms based on intuition and some through brainstorming processes \autocite{vaughan2014web}. In this study our choice of search term took into account the list of distance learning solutions published by UNESCO \autocite{unesco2020DLsolutions}. Eventhough, the solutions they had recommended do not carry their explicit endorsement, they tend to have a wide reach, a strong user-base and evidence of impact \autocite{unesco2020DLsolutions}. For each keyword, the worldwide search queries were performed with a keyword being used as the ``search term''. That allowed us to search the exact string of text typed by the user. However, according to \textcite{vaughan2014web}, short forms or acronyms had higher search volumes than the corresponding complete names, in general. However, we did not use the acronym in this study, as our focus is on specific tools and techniques available in the market to fulfill distance education needs and acronyms could be confused with another entity.

We did our analysis under 11 sub segmentation namely, digital learning management systems, systems built for use on basic mobile phones, systems with strong offline functionality, Massive Open Online Course (MOOC) Platforms, self-directed learning content, mobile reading applications, collaboration platforms that support live-video communication, tools for teachers to create of digital learning content, external repositories of distance learning solutions, tools for online proctoring and Resources to provide psychosocial support. The segmentation was mainly motivated by the list of distance learning solutions published by UNESCO in response to COVID-19 pandemic.

In google trends, it is possible to search for only up to five queries at a time \autocite{vaughan2014web}. Therefore, under each segmentation we entered up to five distance learning tools at a time and recorded their relative ranking scores. An iterative pairwise comparison was first used to identify the series that has highest search volume during the study period. Through this iterative process of relative comparison, we were able to identify the tool with the highest relative ranking score. Then the relative ranking scores for all the other tools in the given segmentation was obtained relative to the previously detected series with the highest ranking scores \autocite{vaughan2014web}.

Both visual and analytical approaches were used to analyse the changes in web search queries at the global level to identify the emerging evidence about the impact of COVID-19 pandemic on distance education. We also evaluated the relationship between weekly web searches and the number of weekly global cases of COVID-19. Cross correlation analysis and the dynamic time warping algorithm \autocite{giorgino2009computing} were performed to investigate the relationship and similarities between the signatures of COVID-19 related search volume data and distance education related search volume data.

>>>>

In this work, we also used Google Trend search queries as a measurement proxy to investigate emerging evidence about distance learning and the popularity and public interest in various distance education solutions. We used weekly Google Trends search queries of various distance learning solutions during COVID-19 pandemic. We limited all of our searches to the period from 1 December 2019 to 15 August 2021 to match the period of COVID-19 pandemic. Through this we wanted to capture the volume of interest in the public realm about distance education solutions and how this changes over time.

Google Trends determines categories based on search patterns. According to \textcite{vaughan2014web} more relevant and accurate data can be obtained by limiting the search in Google Trends to a specific category as it helps to reduce noise in the data. In this work, our focus was given to the education category. Google Trends does not provide the absolute search volume of a given search term. Instead, it provides the relative search volume of a particular term, adjusted according to the total searches of the geography and time range it represents. The resulted series scales from 0 to 100, where each data point in the series represents the search interest relative to the highest point in the series for the selected region and time. \autocite{alicino2015assessing,vaughan2014web}. As such, a value of 100 represents the peak popularity of the term.

It is important to decide what term to search for in Google Trends as different terms have different search volumes. In the past, several strategies have been used to select suitable search terms for a given study. Some studies have selected search terms based on intuition and some through brainstorming processes \autocite{vaughan2014web}. In this study, our choice of search term took into account the list of distance learning solutions published by UNESCO \autocite{unesco2020DLsolutions}. Even though, the solutions they have recommended do not carry their explicit endorsement, they tend to have a wide reach, a strong user-base, and evidence of impact \autocite{unesco2020DLsolutions}. For each keyword, the worldwide search queries were performed with the keyword being used as the ``search term''. That allowed us to search for the exact string of text typed by the user. However, according to \textcite{vaughan2014web}, short forms or acronyms had higher search volumes than the corresponding complete names, in general. However, we did not use the acronym in this study, as our focus is on specific tools and techniques available in the market to fulfill distance education needs, and acronyms could be confused with another entity.

We did our analysis under 11 sub-segments namely, digital learning management systems, systems built for use on basic mobile phones, systems with strong offline functionality, Massive Open Online Course (MOOC) platforms, self-directed learning content, mobile reading applications, collaboration platforms that support live-video communication, tools for teachers to create digital learning content, external repositories of distance learning solutions, tools for online proctoring, and resources to provide psychosocial support. The segmentation was mainly motivated by the list of distance learning solutions published by UNESCO in response to the COVID-19 pandemic.

In Google trends, it is possible to search for only up to five queries at a time \autocite{vaughan2014web}. Therefore, under each segmentation, we entered up to five distance learning tools at a time and recorded their relative ranking scores. An iterative pairwise comparison was first used to identify the series that had the highest search volume during the study period. Through this iterative process of relative comparison, we were able to identify the tool with the highest relative ranking score. Then the relative ranking scores for all the other tools in the given segmentation were obtained relative to the previously detected series with the highest ranking scores \autocite{vaughan2014web}.

Both visual and analytical approaches were used to analyse the changes in web search queries at the global level to identify the emerging evidence about the impact of the COVID-19 pandemic on distance education. We also evaluated the relationship between weekly web searches and the number of global cases of COVID-19. Cross correlation analysis and the dynamic time warping algorithm \autocite{giorgino2009computing} were performed to investigate the relationship and similarities between the signatures of COVID-19 related search volume data and distance education related search volume data.

### 2021-12-28 main.Rmd
updated methodology

In this work we also used  Google Trend search quiries   as a measurement proxy to investigate  emerging evidence about  distance learning and the popularity and the public interest in various distance education solutions. We used weekly  Google Trend search quiries of various distance learning solutions during COVID-19 pandemic. We limited all of our searches to the period from 1 December 2019 to 15 August 2021 to match the  period of COVID-19 pandemic.  Through this we wanted to capture the volume of interest in the public realm about distance education solutions and how this changes over time.

Google Trends determines categories based on search patterns. According to @vaughan2014web  more relevant accurate data can be obtained by  limiting the search in Google Trends to a specific category as it helps  to reduce noise in the data. In this work our focus was given to education category. Google Trends does not provide the absolute search volume of a given search term. Instead it provides a relative search volume of a  particular term adjusted according to  the total searches of the geography and time range it represents. The resulted series  scale from 0 to 100, where each data point in the series represents the search interest relative to the highest point on the series for the selected region and time. [@alicino2015assessing; @vaughan2014web]. As such, a value of 100 represents the peak popularity of the term.

It is important to decide what term to search for in Google Trends as different terms have different search volumes. In the past literature several strategies have been used to select suitable search terms for a given study. Some studies have  selected search terms based on intuition and some through  brainstorming processes [@vaughan2014web]. In this study our choice of search term  took into account the list of distance learning solutions published by UNESCO [@unesco2020DLsolutions].  Eventhough, the solutions they had recommended do not carry their explicit endorsement, they tend to have a wide reach, a strong user-base and evidence of impact [@unesco2020DLsolutions].  For each keyword, the worldwide search queries were performed with a keyword being used  as the "search term". That allowed us to search the exact string of text typed by the user. However, according to @vaughan2014web,  short forms or acronyms had higher search volumes than the corresponding complete names, in general. However, we did not  use the acronym in this study, as our focus is on specific tools and techniques available in the market to fulfill distance education needs and acronyms could be confused with another entity.

We did our analysis under 11 sub segmentation namely, digital learning management systems, systems built for use on basic mobile phones, systems with strong offline functionality,  Massive Open Online Course (MOOC) Platforms, self-directed learning content, mobile reading applications, collaboration platforms that support live-video communication, tools for teachers to create of digital learning content, external repositories of distance learning solutions, tools for online proctoring and Resources to provide psychosocial support. The segmentation was mainly motivated by the list of distance learning solutions published by UNESCO in response to COVID-19 pandemic.

In google trends, it is possible to search for only up to five queries at a  time [@vaughan2014web]. Therefore, under each segmentation we entered up to five distance learning tools at a time and recorded their relative ranking scores. An iterative pairwise comparison was first used to identify the series that has highest search volume during the study period. Through this iterative process of relative comparison, we were able to identify the tool with the highest relative ranking score. Then the relative ranking scores for all the other tools in the given segmentation was obtained relative to the previously detected series with the highest ranking scores [@vaughan2014web].

Both visual and analytical approaches were used to  analyse the changes in web search queries at the global level to identify the emerging evidence about the impact of  COVID-19 pandemic on distance education.  We also evaluated the  relationship between weekly web searches and the number of  weekly global cases of COVID-19. Cross correlation analysis and  the dynamic time warping algorithm [@giorgino2009computing] were performed  to investigate the relationship and similarities between the signatures of  COVID-19 related search volume data  and distance education related search volume data.

>>>>

In this work, we also used  Google Trend search queries   as a measurement proxy to investigate  emerging evidence about  distance learning and the popularity and public interest in various distance education solutions. We used weekly  Google Trends search queries of various distance learning solutions during COVID-19 pandemic. We limited all of our searches to the period from 1 December 2019 to 15 August 2021 to match the  period of COVID-19 pandemic.  Through this we wanted to capture the volume of interest in the public realm about distance education solutions and how this changes over time.

Google Trends determines categories based on search patterns. According to @vaughan2014web  more relevant and accurate data can be obtained by limiting the search in Google Trends to a specific category as it helps to reduce noise in the data. In this work, our focus was given to the education category. Google Trends does not provide the absolute search volume of a given search term. Instead, it provides the relative search volume of a  particular term, adjusted according to  the total searches of the geography and time range it represents. The resulted series  scales from 0 to 100, where each data point in the series represents the search interest relative to the highest point in the series for the selected region and time. [@alicino2015assessing; @vaughan2014web]. As such, a value of 100 represents the peak popularity of the term.

It is important to decide what term to search for in Google Trends as different terms have different search volumes. In the past, several strategies have been used to select suitable search terms for a given study. Some studies have  selected search terms based on intuition and some through  brainstorming processes [@vaughan2014web]. In this study, our choice of search term  took into account the list of distance learning solutions published by UNESCO [@unesco2020DLsolutions].  Even though, the solutions they have recommended do not carry their explicit endorsement, they tend to have a wide reach, a strong user-base, and evidence of impact [@unesco2020DLsolutions].  For each keyword, the worldwide search queries were performed with the keyword being used  as the "search term". That allowed us to search for the exact string of text typed by the user. However, according to @vaughan2014web,  short forms or acronyms had higher search volumes than the corresponding complete names, in general. However, we did not  use the acronym in this study, as our focus is on specific tools and techniques available in the market to fulfill distance education needs, and acronyms could be confused with another entity.

We did our analysis under 11 sub-segments namely, digital learning management systems, systems built for use on basic mobile phones, systems with strong offline functionality,  Massive Open Online Course (MOOC) platforms, self-directed learning content, mobile reading applications, collaboration platforms that support live-video communication, tools for teachers to create digital learning content, external repositories of distance learning solutions, tools for online proctoring, and resources to provide psychosocial support. The segmentation was mainly motivated by the list of distance learning solutions published by UNESCO in response to the COVID-19 pandemic.

In Google trends, it is possible to search for only up to five queries at a  time [@vaughan2014web]. Therefore, under each segmentation, we entered up to five distance learning tools at a time and recorded their relative ranking scores. An iterative pairwise comparison was first used to identify the series that had the highest search volume during the study period. Through this iterative process of relative comparison, we were able to identify the tool with the highest relative ranking score. Then the relative ranking scores for all the other tools in the given segmentation were obtained relative to the previously detected series with the highest ranking scores [@vaughan2014web].

Both visual and analytical approaches were used to  analyse the changes in web search queries at the global level to identify the emerging evidence about the impact of  the COVID-19 pandemic on distance education.  We also evaluated the  relationship between weekly web searches and the number of global cases of COVID-19. Cross correlation analysis and  the dynamic time warping algorithm [@giorgino2009computing] were performed  to investigate the relationship and similarities between the signatures of  COVID-19 related search volume data  and distance education related search volume data.
